Describing the scale and composition of calls for police service: a replication and

### 2022-02-08 paper.Rmd
paper backup

Here, we propose an extension of @ratcliffe2021policing and @lum2021can. This extension is motivated by three principal components. First, we replicate the main analyses of these existing investigations into the scale and composition of police demand using open study materials. To date, investigations have been conducted on data which is not publicly available and without the materials (e.g., code) to reproduce the results. Yet, open science practices have been identified as fundamental to the aims of evidence-based policing and vital in ensuring that real-life decisions are made based on a concrete pool of evidence [@openedp2019]. In this case. the necessity for a fully open investigation into the scale and composition of police demand is perhaps especially important given the public nature of debate around police reform and the considerable implications of redefining the role of the police without transparent empirical investigation. It is reasonable for police practitioners and the public to expect a thorough, open and replicable investigation into police demand across different contexts before academia concludes that the issue is resolved – certainly before findings are used to change or introduce police practice or public policy.

@@

That said, a notable shortcoming of these recent contributions is the lack of openly available data and code to reproduce and replicate findings. This is not an uncommon issue in policing research. A recent scoping review of Canadian policing studies concluded that there has been "little effort... to replicate or reproduce findings", with just 8% of the literature sampled constituting replications or reproductions [@huey2017replication, p. 113]. More broadly, in a sample of papers from top criminology journals, @mcneeley2015replication found that just 2% of papers were replications -- either a direct replication of the same population, or empirical generalizations from a different population. Yet, the practice of open science is fundamental in achieving the goals of evidence-based policing, namely, "to develop a rigorous evidence base that can be used by police professionals to develop more efficient and effective police practices, policies, and/or programs" [@openedp2019, p. 126]. Comparable statements have been made in related fields, such as science [@laycock2013defining]. It therefore seems appropriate that the investigations of @ratcliffe2021policing and @lum2021can are replicated using open data and methods.

One reason to hesitate over conducting such a replication is that these two existing studies were descriptive accounts of police demand in specific study sites. In scientific research more broadly, replications are often motivated by the need to check for Type I or Type II errors using a different sample from the same population and/or adjust for control variables which may have influenced the dependent variable of interest [@gross1997need; see also @mackey2012or]. We might therefore conclude that a replication of @ratcliffe2021policing and @lum2021can is unwarranted: instead, replications should be reserved only for those studies deploying experimental designs or inferential statistics from a random sample, the conclusions from which will be generalized to a population. We disagree. There are plentiful reasons to conduct an open descriptive investigation into the scale and composition of police demand. This is for two principal reasons.

the descriptive findings from @lum2021can, without the use of random sampling and inferential statistics, are already being generalized to the United States as a whole. This is most evident in _The Washington Post_ article [@lumwash].

the implications of redefining the role of the police is considerable.

It is reasonable for police practitioners and the public to expect a thorough, open and replicable empirical investigation into police demand across numerous contexts before academia concludes that the issue is resolved. B

certainly before findings are used to change or introduce police practice or public policy. As noted, committing to radical reform without such investigations might result in shifts in public demand for services for which there is no suitable supply.

Second, the data handling required to describe the public demand for the police is not straightforward. Reporting the scale and composition of emergency calls for service data necessitates the grouping of incident types through categorization (e.g., 'mental health', 'community'). As both @ratcliffe2021policing and @lum2021can point out, categorizing incident types is challenging and subject to a degree of interpretation. This issue is exacerbated by the fact that different police jurisdictions will use different incident categories. Thus, an open replication, inclusive of the categorization decisions, facilitates scrutiny through transparency and provides robustness to existing findings.

With these points in mind, this paper describes the emergency demand for police services in a large city, Detroit, US, using open data and open code. All materials are publicly available (see https://anonymous.4open.science/r/demand_detroit-FCD3/README.md). It does so in replication, and where appropriate extension, of the main findings reported by @ratcliffe2021policing and later @lum2021can. In this way, the contribution serves to test the robustness of existing findings, but also provides the materials required to reproduce and replicate analyses in the interests of transparency and public scrutiny.

>>>>

Here, we propose an extension of @ratcliffe2021policing and @lum2021can. This extension is motivated by three principal components. First, we replicate the main analyses of these existing investigations into the scale and composition of police demand using open study materials. To date, investigations have been conducted on data which is not publicly available and without the materials (e.g., code) to reproduce the results. Yet, open science practices have been identified as fundamental to the aims of evidence-based policing and vital in ensuring that in the long-term, real-life decisions are based on a concrete pool of evidence [@openedp2019]. In this case. the necessity for a fully open investigation into the scale and composition of police demand is perhaps especially important given the public nature of debate around police reform and the considerable implications of redefining the role of the police without transparent empirical investigation. It is reasonable for police practitioners and the public to expect a thorough, open and replicable investigation into police demand across different contexts before academia concludes that the issue is resolved – certainly before findings are used to change or introduce police practice or public policy.

@@

With these points in mind, this paper describes the emergency demand for police services in a large city, Detroit, US, using open data and open code. All materials are publicly available (see https://anonymous.4open.science/r/demand_detroit-FCD3/README.md). It does so in replication, and where appropriate extension, of the main findings reported by @ratcliffe2021policing and later @lum2021can. In this way, the contribution serves to test the robustness of existing findings, but also provides additional insight through new analyses, and provides the materials required for reproduction and replication in the interests of transparency and public scrutiny.
